Tracing the cultural evolution of meaning at the semantics-pragmatics interface

### 2017-03-17 paper/paper-v3.tex
tentative revision draft with correct plots

\begin{figure}
\centering
\includegraphics[width=1\textwidth,height=8cm,keepaspectratio]{./plots/fig1-onlyr}
\caption{Proportion of pragmatic $\Llack$-style types and incumbent types in $5$ independent populations after $50$ generations under only a pressure for expressivity.}
\label{fig:only-R}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=1\textwidth,height=8cm,keepaspectratio]{./plots/fig2-onlym-pr}
\caption{Proportion of pragmatic $\Llack$-style types and incumbent types in $5$ independent populations after $50$ generations under only a pressure for learnability ($\lambda = 20, k = 5$). The types' prior probability is shown in the right-most plot.}
\label{fig:only-M}
\end{figure}

The effect of iterated learning without a pressure for expressivity using posterior sampling ($l = 1$) and a stronger tendency towards posterior maximization ($l = 15$) is shown in Figure \ref{fig:only-M} together with the prior over types. The latter illustrates that users of $\Llack$ are, while not the most favored types, advantaged by the inductive bias in virtue of the relatively simple semantics they conventionalize. Accordingly, a stronger propensity to maximize the posterior increases their proportion in the population in analogous fashion to increase in $\lambda$ under the replicator dynamic. However, while replication generally succeeds in driving out competing types of a kind, iterated learning leads to their coexistence as each of these types is passed on to next generations equal faithfulness. Although $\Llack$ is not the most favored type by the prior, it is the least semantically complex language in the type space that enables its users to convey each state with a single message when combined with pragmatic reasoning (provided sufficiently high $\lambda$). Put differently, it is easier to infer than functionally comparable lexica such as $\Lbound$ and it is less likely to be mistaken with others because its pragmatic use approximates a one-to-one form-meaning mapping. Consequently, as suggested by Figure \ref{fig:only-M}, in $1000$ analyzed independent populations all incumbents were pragmatic $\Llack$ users provided sufficient rationality and a tendency towards posterior maximization ($l = 15$, $\lambda = 20$). By contrast, low values of $\lambda$ and $l$ reflect the inductive bias more directly, favoring functionally deficient but a priori preferred types such as literal $\Lall$. In the extreme, all out of $1000$ independent populations had this type as incumbent ($\lambda = 1$,$l = 1$).

\subsubsection{Expressivity and learnability.}
Inspecting these pressures separately not only showcases the contribution of the model's components but also highlights some of their broader implications. First and foremost, neither dynamic on its own comes close to converging to a monomorphic population of a type of pragmatic $\Llack$ speakers. On the one hand, the slight communicative advantage of $\Lbound$'s lexicalization of an upper-bound over pragmatic use of $\Llack$ leads to the former's selection under a pressure for expressivity. On the other hand, pressure only towards learnability has a modest but clear effect of promoting pragmatic $\Llack$ over functionally similar but semantically more complex alternatives such as $\Lbound$. However, on its own learnability does not strongly foment the propagation of these types across the population. Furthermore, this pressure alone leads to heterogeneous populations that do not justify the selection of a particular type over others.

Figure \ref{fig:rmd} illustrates the combined effects of both pressures for a sample of $\lambda$ and $l$ values. Overall, these results show that an inductive learning bias for simpler semantics in tandem with functional pressure can lead to the selection of $\Llack$-like semantics over $\Lbound$. As when each pressure was considered in isolation, this effect increases with $\lambda$ and $l$. Importantly and by contrast to the effects of learnability alone, the addition of a pressure towards expressivity magnifies this effect and dampens the proliferation of similar or identical types. As stressed above, this suggests that neither a learning bias nor functional pressure alone but their combination may lead to the lack of upper-bounds in the lexical meaning of scalar expressions in a mostly monomorphic population. \tb{However, not even its combination with a pressure for expressivity completely drives out competing types under this inference strategy. This is not so for stronger posterior maximizing learning. The proportion to which a single pragmatic $\Llack$-style type increases grows with MAP-like learning. }

\begin{figure}
\centering
\includegraphics[width=1\textwidth,height=8cm,keepaspectratio]{./plots/fig3-r+m}
\caption{Proportion of pragmatic $\Llack$-style types and incumbent types in $5$ independent populations after $50$ generations under both pressures ($k = 5$).}
\label{fig:rmd}
\end{figure}

As before, low $\lambda$ and $l$ lead to the incumbency of communicatively suboptimal types that learners are biased for, such as $\Lall$. An increase in $\lambda$ leads to the selection and incumbency of pragmatic $\Llack$ types but does not lead to monomorphic populations if learners sample from the posterior. Finally, a combination of sufficiently rational signaling behavior with some tendency for posterior maximization leads to increasingly monomorphic populations of types that convey upper-bounds pragmatically. A more succinct representation of the difference between the mean of the highest pragmatic $\Llack$-like types and the highest proportion of other types across $\lambda$ and $l$ values is given in Figure \ref{fig:diff}.

\begin{figure}
\centering
\includegraphics[width=1\textwidth,height=8cm,keepaspectratio]{./plots/fig4-incumbents-difference}
\caption{Difference between mean proportion of highest pragmatic $\Llack$ type and highest other type in $1000$ independent populations after $50$ generations under both pressures ($k = 5$).}
\label{fig:diff}
\end{figure}

@@

\subsection{Discussion}
Under the assumption of a learning bias for simpler lexical representations, our results suggest that a lack of semantic upper-bounds coupled with pragmatic reasoning can overcome communicative pressures and stabilize in a population. This prediction hinges on three assumptions. First, that language is pressured toward both expressivity and learnability. Second, that language use is relatively deterministic. Lastly, that learners prefer simpler over more complex lexical representations. An important addendum to this third condition being that a combination of rationality in choice and maximization in learning requires a weaker bias towards simplicity. Under these conditions the selection of lexical meanings lacking upper-bounds in populations of pragmatic speakers is robust against parameter perturbations.  This outcome is particularly encouraging in light of other advantages a lack of semantic upper-bounds may confer, as discussed at the beginning of Section \ref{sec:si-case-study}.

A lack of upper-bounded in the lexical meaning of weak scalar expressions constitutes the majority view in the literature. However, it not clear to what extent other types should be present in the final population. It seems reasonable to expect functionally suboptimal types $L_1$, $L_2$ and $L_3$ to be ruled out because they fail to enable their users to communicate effectively. However, this is not true of $L_4$.\footnote{$L_6$ presents a special case. In our current setup, it mirrors $L_5$ in enabling for the pragmatic strengthening of a message that does not codify an upper-bound lexically. However, this is achieved by ruling out $\ssome$ and not, as with scalar implicatures, $\sall$. $L_6$ speakers therefore strengthen a ``some''-message to convey something paraphrasable as `some but not [some but not all]'. The current representation of lexica as Boolean matrices is blind to this anomaly.} The prediction that natural language communities are homogeneous or that a single speaker may entertain $L_4$-like semantics for one scalar expression and $L_5$-like semantics for another is not implausible (cf. \citealt{franke+degen:2016}). Alternatively, a stronger tendency for posterior maximization has to be assumed (see Figure \ref{fig:prior-posterior}). This empirical issue relates to other two aspects left undiscussed: disadvantages of pragmatic reasoning and the effect of state frequencies on the fossilization of pragmatic inferences. We tacitly assumed pragmatic reasoning to come at no cost. However, there is experimental evidence that suggests  that the pragmatic derivation of upper-bounds costs effort and takes additional processing time (cf. \citealt{deNeys+schaeken:2007, huang+snedeker:2009}). This raises the question at which point such usage-based cost undercuts the learnability advantage of simpler semantic representations. Should cost play a role, then its effect is bound to depend on the frequency with which a given scalar expression is used. It is therefore plausible that frequently drawn scalar implicatures might fossilize to avoid cost, while infrequent ones are still derived on-line. This also opens a possible venue to address the preceding question about the expected presence of $L_4$-like semantics, but further empirical evidence is needed to assess these matters beyond speculation.

\section{General discussion}\label{sec:discussion}
We laid out a model that combines game theoretical models of functional pressure towards efficient communication \citep{nowak+krakauer:1999}, effects of transmission perturbations on (iterated) language learning \citep{griffiths+kalish:2007}, probabilistic speaker and listener types of varied degrees of pragmatic sophistication \citep{frank+goodman:2012, franke+jaeger:2014} as well as different lexica \citep{bergen+etal:2012,bergen+etal:2016}. This model generates predictions about lexicalization patterns and, more generally, effects of communicative pressures on the cultural evolution of language.

We argued that the puzzle raised by semantics in light of pragmatics is hard to explain on purely functional grounds and that part of the answer may instead lie in the way transmission shapes the outcome of cultural evolution in tandem with a pressure for successful information transfer. In the realm of inductive biases, we adopted the assumption that simpler semantic representations are more likely to be learned (cf. \citealt{chater+vitanyi:2003}). Under this view, semantics and pragmatics play a synergic role in that representational simplicity is supplemented by pragmatic reasoning to counteract functional disadvantages otherwise incurred. As a consequence, iterated transmission and use of language lead to a regularization that may explain the lack of lexicalization of systematic pragmatic enrichments. This result is of particular relevance for the longstanding assumption of a divide and interaction between semantics and pragmatics. It offers an account of why (certain) pragmatic inferences fail to lexicalize. More generally, we showed that systematic noise in perception can produce outcomes that are similar from those generated by inductive biases.

The main innovations of the model are its modular separation of expressivity and learnability, allowing for their isolated and combined analysis, the learning process involving a joint inference over types of pragmatic behavior and lexical meaning, as well as in its accommodation of different transmission perturbations that go beyond learning biases. The goal to decouple but model both expressivity and learnability has also recently been addressed by \citet{kirby+etal:2015}. In contrast to our proposal, Kirby et al. model expressivity as exerting its force only in the production of learning data. This model's expressivity parameter thereby fulfills a similar role  to high values of $\lambda$ in making speaker behavior more deterministic. In this way, it ``favors'' unambiguous languages. However, the degree of mutual understanding of interlocutors central to replication and to our notion of expressivity is not taken into consideration. That is, while our proposal combines bidirectional horizontal transmission with its vertical and unidirectional counterpart, Kirby et al.'s model only considers the latter's influence. Our reasoning behind the inclusion of the former lies in the empirical and theoretical observation that learnability alone can lead the selection of functionally defective languages, as illustrated by the tautological language $L_3$ in our analysis. This outcome has been reported in a number of laboratory experiments where the participants' task was to learn and subsequently reproduce the language produced by a previous participant, leading to a proliferation of languages that associated a large number of meanings with a single form (see e.g. \citealt{silvey+etal:2014} and experiment 1 in \citealt{kirby+etal:2008}). In contrast, experiments involving an interactive component have been found to foster languages that enable interlocutors to distinguish meanings more accurately  (e.g. \citealt{fay+etal:2013}; for a review of laboratory results under the iterated learning paradigm and further discussion see \citealt{kirby+etal:2015, tamariz+kirby:2016}). It is not evident how to compare these empirical findings given that they consider distinct meaning spaces, modes of transmission, iterations and feedback given to participants. However, we take these results to suggest that there is an important difference between a language generating learnable linguistic data and its actual performance as a means of information transfer. The former solely depends on the mechanism by which speakers associate form and meaning. The latter additionally hinges on the addressee's linguistic experience and her ability to interpret linguistic input based on this experience. In sum, we contend that successful information transfer in a linguistic community is central to the adoption of a communication system and that this measure is not adequately reflected by production alone.

The demonstration that noise can lead to regularized evolutionary outcomes that are similar to those generated by prior learning biases is relevant not for the case study at hand, but more so for the broader project of investigating the cultural evolution of language. On the one hand, the plurality of sources of transmission perturbations admitted by these models paints a cautionary tale for the design of studies that purport to provide explanatory accounts of linguistic phenomena. In particular when the outcome is interpreted as being informative about the perturbation assumed to generate it (cf. \citealt{tamariz+kirby:2016}). On the other, and most importantly, it showcases how regularities can arise as a byproduct of systematic noise rather than from standardly assumed inductive biases.

\section{Conclusion}
The cultural evolution of language is influenced by intertwined pressures. We set out to investigate this process by putting forward a model that combines a pressure toward efficient and successful information transfer with perturbations that may arise in the transmission of linguistic knowledge in acquisition. Additionally, we argued for the necessity of considering the role of pragmatics in investigations on the cultural evolution of meaning. These components and their mutual influence were highlighted in a case study on the lack of lexical upper-bounds in weak scalar expressions that showed that, when pressured for learnability and expressivity, the former drives for simpler semantic representations inasmuch as pragmatics can compensate for lack of expressivity in use. That is, the relative learning advantage of simpler semantics in tandem with a functional pressure in use may offer an answer to why natural languages fail to lexicalize systematic pragmatic inferences.

We also considered an alternate instantiation of the model, which shows that systematic noise in state perception can give rise to evolutionary outcomes that are similar to those predicted by inductive biases. This stresses the fact that that learning and typology are not necessarily close reflections of each other \citep{bowerman:2010}. In particular, language use and environmental factors can play an important role in language change, making them central variables in explanatory accounts of natural language properties.

>>>>

\begin{figure}
\centering
\includegraphics[width=\textwidth,height=8cm, keepaspectratio]{./plots/fig1-onlyr}
\caption{Stacked proportion of pragmatic $\Llack$-style types and incumbent types, when other than pragmatic $\Llack$, in $5$ independent populations after $50$ generations under only a pressure for expressivity.}
\label{fig:only-R}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=1\textwidth,height=8cm,keepaspectratio]{./plots/fig2-onlym-pr}
\caption{Stacked proportion of pragmatic $\Llack$-style types and incumbent types, when other than pragmatic $\Llack$, in $5$ independent populations after $50$ generations under only a pressure for learnability ($\lambda = 20, k = 5$). The types' prior probability is shown in the right-most plot.}
\label{fig:only-M}
\end{figure}

The effect of iterated learning without a pressure for expressivity with posterior sampling ($l = 1$) and a stronger tendency towards posterior maximization ($l = 15$) is shown in Figure \ref{fig:only-M} together with the prior over types. The latter shows that while users of $\Llack$ are not the most favored by the inductive bias (compared, e.g., to $\Lall$) they are nevertheless advantaged in virtue of the relatively simple semantics they conventionalize (compared, e.g., to $\Lbound$). Additionally, $\Llack$ enables its users to convey each state with a single message when combined with pragmatic reasoning provided sufficiently high $\lambda$. This makes it less likely to be confused with other types if the data is not too sparse ($k \geq 5$). Put differently, learners have a higher propensity to infer pragmatic $\Llack$ over types that might be hard or impossible to distinguish it from based on overt linguistic behavior, such as $\Lbound$, and $\Llack$ is also less likely to be mistaken with types with different linguistic behaviors because its pragmatic use approximates a one-to-one form-meaning mapping. As a consequence, a stronger propensity to maximize the posterior increases their proportion in the population. However, while we showed replication to generally succeed in driving out competing types of a kind, e.g., different pragmatic $\Llack$-style types, iterated learning leads to their coexistence as each of these types is passed on to next generations equal faithfulness and they do not stand in competition with each other. As already suggested by Figure \ref{fig:only-M}, in $1000$ analyzed independent populations all incumbents were pragmatic $\Llack$ users provided sufficient rationality and a tendency towards posterior maximization ($l = 15$, $\lambda = 20$). By contrast, low values of $\lambda$ and $l$ reflect the learners' inductive bias more directly, favoring functionally deficient but a priori preferred types such as literal $\Lall$. In the extreme, when $l = 1$ and $\lambda = 1$ all of $1000$ independent populations had $\Lall$ as incumbent.

\subsubsection{Expressivity and learnability.}
Inspecting these pressures separately not only showcases the contribution of the model's components but also highlights some of their broader implications. First and foremost, neither dynamic on its own comes close to converging to a monomorphic population of pragmatic $\Llack$ speakers. On the one hand, the slight communicative advantage of $\Lbound$'s lexicalization of an upper-bound over pragmatic use of $\Llack$ leads to the former's selection under a pressure for expressivity. On the other hand, pressure only towards learnability has a modest but clear effect of promoting pragmatic $\Llack$ over functionally similar but semantically more complex alternatives such as $\Lbound$. However, on its own learnability does not foment the propagation of these types across the population. Furthermore, this pressure alone leads to heterogeneous populations that do not justify the selection of a particular type over others.

\begin{figure}
\centering
\includegraphics[width=1\textwidth,height=8cm,keepaspectratio]{./plots/fig3-r+m}
\caption{Stacked proportion of pragmatic $\Llack$-style types and incumbent types, when other than pragmatic $\Llack$, in $5$ independent populations after $50$ generations under both pressures ($k = 5$).}
\label{fig:rmd}
\end{figure}

Figure \ref{fig:rmd} illustrates the combined effects of both pressures for a sample of $\lambda$ and $l$ values. These results show that an inductive learning bias for simpler semantics in tandem with functional pressure can lead to the selection of $\Llack$-like semantics over $\Lbound$. As when each pressure was considered in isolation, the proportion of these types increases with $\lambda$ and $l$. Crucially, the addition of a pressure towards expressivity magnifies the learning outcome and dampens the proliferation of similar or identical types. As stressed above, this suggests that neither a learning bias nor functional pressure alone but their combination may lead to the lack of upper-bounds in the lexical meaning of scalar expressions in a mostly monomorphic population.

As before, low $\lambda$ and $l$ lead to the incumbency of communicatively suboptimal types that are a priori favored by learning, such as $\Lall$. An increase in $\lambda$ leads to the selection and incumbency of pragmatic $\Llack$ types but does not lead to monomorphic populations if learners sample from the posterior. Finally, a combination of sufficiently rational signaling behavior with some tendency for posterior maximization leads to increasingly monomorphic populations of types that convey upper-bounds pragmatically. A more succinct representation of the difference between the mean of the highest pragmatic $\Llack$-like types and the highest proportion of other types across $\lambda$ and $l$ values is given in Figure \ref{fig:diff}. \tb{Say more}

\begin{figure}
\centering
\includegraphics[width=1\textwidth,height=6cm,keepaspectratio]{./plots/fig4-incumbents-difference}
\caption{Difference between mean proportion of highest pragmatic $\Llack$ type and highest other type in $1000$ independent populations after $50$ generations under both pressures ($k = 5$).}
\label{fig:diff}
\end{figure}

@@

\subsection{Discussion}
Under the assumption of a learning bias for simpler lexical representations, our results suggest that a lack of semantic upper-bounds coupled with pragmatic reasoning can overcome communicative pressures and be majoritarily selected for in a population. This prediction hinges on three assumptions. First, that language is pressured toward both expressivity and learnability. Second, that language users favor expressions/interpretations expected to have a higher likelihood of being understood/meant over ones with a lower likelihood. Lastly, that learners prefer simpler over more complex lexical representations and exhibit a tendency towards the acquisition of the type that best explains the learning data. This outcome is particularly encouraging in light of other advantages a lack of semantic upper-bounds may confer, as discussed at the beginning of this section.

A lack of upper-bounded in the lexical meaning of weak scalar expressions constitutes the majority view in the literature. However, it not clear to what extent other types should be present in the final population. It seems reasonable to expect functionally suboptimal lexica such as $\Lall$ to be ruled out because they fail to enable their users to communicate effectively and are not evinced in natural language. However, this is not true of $\Lbound$. The prediction that natural language communities are homogeneous or that a single speaker may entertain $\Llack$-like semantics for one scalar expression and $\Lbound$-like semantics for another is not implausible (cf. \citealt{franke+degen:2016}). Alternatively, a stronger tendency for posterior maximization in learning has to be assumed. This empirical issue relates to other two aspects left undiscussed: disadvantages of pragmatic reasoning and the effect of state frequencies on the fossilization of pragmatic inferences. We tacitly assumed pragmatic reasoning to come at no cost. However, there is experimental evidence that suggests  that the pragmatic derivation of upper-bounds costs effort and takes additional processing time (cf. \citealt{deNeys+schaeken:2007, huang+snedeker:2009}). This raises the question at which point such usage-based cost undercuts the learnability advantage of simpler semantic representations. Should cost play a role, then its effect is bound to depend on the frequency with which a given scalar expression is used. It may be that frequently drawn scalar implicatures fossilize to avoid cost whereas infrequent ones are still derived on-line. This also opens a possible venue to address the preceding question about the expected presence of $\Lbound$-like semantics in a population, but further empirical evidence is needed to assess these matters.

\section{General discussion}\label{sec:discussion}
We laid out a model that combines game theoretical models of functional pressure towards efficient communication \citep{nowak+krakauer:1999}, effects of transmission perturbations on (iterated) language learning \citep{griffiths+kalish:2007}, probabilistic speaker and listener types of varied degrees of pragmatic sophistication \citep{frank+goodman:2012, franke+jaeger:2014} as well as different lexica \citep{bergen+etal:2012,bergen+etal:2016}, and \tb{mention LOT here}. This model generates predictions about lexicalization patterns and, more generally, effects of communicative pressures on the cultural evolution of language.

We argued that the puzzle raised by semantics in light of pragmatics is hard to explain on purely functional grounds and that part of the answer may instead lie in the way transmission shapes the outcome of cultural evolution in tandem with a pressure for successful information transfer. In the realm of inductive biases, we adopted the assumption that simpler semantic representations are more likely to be learned (cf. \citealt{chater+vitanyi:2003}), \tb{mention LOT here}. Under this view, semantics and pragmatics play a synergic role in that representational simplicity is supplemented by pragmatic reasoning to counteract functional disadvantages otherwise incurred. As a consequence, iterated transmission and use of language lead to a regularization that may explain the lack of lexicalization of systematic pragmatic enrichments. This result is of particular relevance for the longstanding assumption of a divide and interaction between semantics and pragmatics by offering an account of why certain pragmatic inferences fail to lexicalize.

The main innovations of the model are its modular separation of expressivity and learnability, allowing for their isolated and combined analysis, the learning process involving a joint inference over types of pragmatic behavior and lexical meaning. The goal to decouple but model both expressivity and learnability has also recently been addressed by \citet{kirby+etal:2015}. In contrast to our proposal, Kirby et al. model expressivity as exerting its force only in the production of learning data. On a general level, this model's expressivity parameter has a similar effect to $\lambda$ in that it can give a communicative advantage to unambiguous languages over ambiguous ones. \tb{Should we go into more detail here? I think it's fine if we leave it out but $\lambda$ has a broad motivation whereas Kirby et al.'s parameter is quite explicitly a penalty parameter against ambiguity. I mainly wanted to give an idea of what the pressure for expressivity in their model does rather than argue for why ours is more principled.} However, the degree of mutual understanding of interlocutors central to replication and to our notion of expressivity is not taken into consideration. That is, while our proposal combines bidirectional horizontal transmission with its vertical and unidirectional counterpart, Kirby et al.'s model only considers the latter's influence. Our reasoning behind the inclusion of the former lies in the empirical and theoretical observation that learnability alone can lead the selection of functionally defective languages, as discussed in relation to $\Lall$ when $\lambda$ or $k$ are low. This outcome has been reported in a number of laboratory experiments where subjects learned and subsequently reproduced the language produced by a previous participant over multiple iterations, leading to a proliferation of ambiguous languages that associate a large number of meanings with a single form (see, e.g., \citealt{silvey+etal:2014} and experiment 1 in \citealt{kirby+etal:2008}). In contrast, experiments involving an interactive component have been found to foster languages that enable interlocutors to communicatively distinguish meanings more accurately  (e.g., \citealt{fay+etal:2013}; for a review of laboratory results under the iterated learning paradigm and further discussion see \citealt{kirby+etal:2015, tamariz+kirby:2016}). It is not evident how to compare these empirical findings given that they consider distinct meaning spaces, modes of transmission, iterations and feedback given to participants. However, we take these results to suggest that there is an important difference between a language generating learnable linguistic data and its actual performance as a means of information transfer. \tb{Explain the next two sentences} The former solely depends on the mechanism by which speakers associate form and meaning. The latter additionally hinges on the addressee's linguistic experience and her ability to interpret linguistic input based on this experience. In sum, we contend that successful information transfer in a linguistic community is central to the adoption of a communication system and that this measure is not adequately reflected by production alone.

\section{Conclusion}
The cultural evolution of language is influenced by intertwined pressures. We set out to investigate this process by putting forward a model that combines a pressure toward efficient and successful information transfer with perturbations that may arise in the transmission of linguistic knowledge in acquisition. \tb{Clarify and put this in better words. This is quite central:} Additionally, we argued for the necessity of considering the role of pragmatics in investigations on the cultural evolution of meaning. These components and their mutual influence were highlighted in a case study on the lack of lexical upper-bounds in weak scalar expressions that showed that, when pressured for learnability and expressivity, the former drives for simpler semantic representations inasmuch as pragmatics can compensate for lack of expressivity in use. That is, the relative learning advantage of simpler semantics in combination with  functional pressure in use may offer an answer to why natural languages fail to lexicalize systematic pragmatic inferences.
